Quality measure notes

### 2021-07-14 StateOfPractice/Ao-Report/13Methods.tex
ao report - minor update

We prefer 30 software packages providing similar functions or falling into different sub-categories depending on our research purpose. So the domain needs to have enough candidates in one sub-category or enough sub-categories to cross-compare.

@@

One factor is the functions and purposes of the software. For example, we can choose a group of software with similar functions, so that the comparison is between the software; or we can cross-compare sub-categories in the domain, then we need to select candidates from each sub-category.

@@

Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the viewer sub-category. We also included MI domain experts in our team.

>>>>

We prefer 30 software packages providing similar functions or falling into different sub-groups depending on our research purpose. So the domain needs to have enough candidates in one sub-group or enough sub-groups to cross-compare.

@@

One factor is the functions and purposes of the software. For example, we can choose a group of software with similar functions, so that the comparison is between the software; or we can cross-compare sub-groups in the domain, then we need to select candidates from each sub-group.

@@

Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the viewer sub-group. We also included MI domain experts in our team.
